% !TEX root = ../SPP_IoTjournal.tex
\subsection{Optimal Avoidance Controller} \label{sec:intruder_avoid}
In this section, our goal is to compute the control policy that a vehicle $\veh_i$ can use to avoid entering in the danger region $\dz_{i\intr}$. We also compute the set of states from which the joint states of $\veh_{\intr}$ and $\veh_i$ can enter the danger zone $\dz_{i\intr}$ despite the best efforts of $\veh_i$ to avoid $\veh_{\intr}$, which is then used to compute the separation region of $\veh_i$ in Section \ref{sec:sepRegion_case1}. 

We define relative dynamics of the intruder $\veh_{\intr}$ with state $\state_\intr$ with respect to $\veh_i$ with state $\state_i$:
\begin{equation}
\label{eq:reldyn}
\begin{aligned}
\state_{\intr i} = \state_\intr - \state_i, \qquad \dot \state_{\intr i} = f_r(\state_{\intr i}, \ctrl_i, \ctrl_\intr, \dstb_i, \dstb_\intr)
\end{aligned}
\end{equation}
Given the relative dynamics, the set of states from which the joint states of $\veh_{\intr}$ and $\veh_{i}$ can enter danger zone $\dz_{i\intr}$ in a duration of $\iat$ despite the best efforts of $\veh_i$ to avoid $\veh_{\intr}$ is given by the backward reachable set $\brs^{\text{A}}_i(\tau, \iat),~ \tau \in [0, \iat]$:
\begin{equation} \label{eqn:avoidBRS}
\begin{aligned}
\brs^{\text{A}}_{i}(\tau, \iat) = & \{y: \forall \ctrl_i(\cdot) \in \cfset_i, \exists \ctrl_\intr(\cdot) \in \cfset_\intr, \exists \dstb_i(\cdot) \in \dfset_i, \\
& \exists \dstb_\intr(\cdot) \in \dfset_\intr, \state_{\intr i}(\cdot) \text{ satisfies \eqref{eq:reldyn}},\\
& \exists s \in [\tau, \iat], \state_{\intr i}(s) \in \targetset^{\text{A}}_{i}, \state_{\intr i}(\tau) = y\},\\
\targetset^{\text{A}}_{i} = & \{\state_{\intr i}: \|\pos_{\intr i}\|_2 \le \rc\}.
\end{aligned}
\end{equation}
The Hamiltonian to compute $\brs^{\text{A}}_{i}(\tau, \iat)$ is given as:
%\begin{equation}
%\begin{aligned}
%H^{\text{A}}_{i}(\state_{\intr i}, \costate) = & \max_{\ctrl_i \in \cset_i} \left( \right.\\
%&\left. \min_{\ctrl_\intr \in \cset_\intr, \dstb_i \in \dset_i, \dstb_\intr \in \dset_\intr} \costate \cdot f_r(\state_{\intr i}, \ctrl_i, \ctrl_\intr, \dstb_i, \dstb_\intr) \right)
%\end{aligned}
%\end{equation}
\begin{equation}
H^{\text{A}}_{i}(\state_{\intr i}, \costate) = \max_{\ctrl_i \in \cset_i} \min_{\substack{\ctrl_\intr \in \cset_\intr, \\ \dstb_\intr \in \dset_\intr, \\ \dstb_i \in \dset_i}} \costate \cdot f_r(\state_{\intr i}, \ctrl_i, \ctrl_\intr, \dstb_i, \dstb_\intr).
\end{equation}
We refer to $\brs^{\text{A}}_i(\tau, \iat)$ as \textit{avoid region} from here on. The interpretation of $\brs^{\text{A}}_{i}(\tau, \iat)$ is that if $\veh_i$ starts inside this set, i.e., $\state_{\intr i}(t) \in  \brs^{\text{A}}_{i}(\tau, \iat)$, then the intruder can force $\veh_i$ to enter the danger zone $\dz_{i\intr}$ within a duration of $(\iat-\tau)$, regardless of the control applied by the vehicle. If $\veh_i$ starts at the boundary of this set (denoted as $\partial \brs^{\text{A}}_{i}(\tau, \iat)$), i.e., $\state_{\intr i}(t) \in  \partial \brs^{\text{A}}_{i}(\tau, \iat)$, it can \textit{barely} successfully avoid the intruder for a duration of $(\iat-\tau)$ using the optimal avoidance control ${\ctrl^{\text{A}}_{i}}$ (referred to as \textit{avoidance maneuver} from here on)
\begin{equation} \label{eqn:optAvoidCtrl}
{\ctrl^{\text{A}}_{i}} = \arg \max_{\ctrl_i \in \cset_i} \min_{\substack{\ctrl_\intr \in \cset_\intr, \\ \dstb_\intr \in \dset_\intr, \\ \dstb_i \in \dset_i}} \costate \cdot f_r(\state_{\intr i}, \ctrl_i, \ctrl_\intr, \dstb_i, \dstb_\intr).
\end{equation}
\noindent Finally, if $\veh_i$ starts outside this set, i.e., $\state_{\intr i}(t) \in \left( \brs^{\text{A}}_{i}(\tau, \iat)\right)^C$, then  $\veh_i$ and $\veh_{\intr}$ cannot instantaneously enter the danger zone $\dz_{i\intr}$, irrespective of the control applied by them at time $t$. In fact, $\veh_i$ can safely apply \textit{any} control as long as it is outside the boundary of this set, but will have to apply the avoidance maneuver to avoid the intruder once it reaches the boundary.

In the worst case, $\veh_i$ might need to avoid the intruder for a duration of $\iat$ starting at $t = \tsa$; thus, the least we must have is that $\state_{\intr i}(\tsa) \in \left(\brs^{\text{A}}_{i}(0, \iat)\right)^C$ to ensure successful avoidance. Otherwise, regardless of what control a vehicle applies, the intruder can force it to enter the danger zone $\dz_{i\intr}$.
\begin{assumption}
\label{as:detection_range}
$\state_{\intr i}(\tsa) \in \left(\brs^{\text{A}}_{i}(0, \iat)\right)^C \forall i \in \{1, \ldots, \N\}$.
\end{assumption}
Intuitively, assumption \ref{as:detection_range} enforces a condition on the detection of the intruder by STP vehicles. For example, if STP vehicles are equipped with circular sensors, then assumption \ref{as:detection_range} implies that STP vehicle must be able to detect a intruder that is within a distance of $\dsen$, where
\begin{equation} \label{eqn:sen_distance}
\dsen = \max\{ \|p_i\|_2: \exists \npos_i, (p_i, \npos_i) \in \brs^{\text{A}}_{i}(0, \iat) \};
\end{equation} 
otherwise, there exists an intruder control strategy such that $\veh_i$ and $\veh_{\intr}$ will collide irrespective of the control used by $\veh_i$. Thus, $\dsen$ is the \textit{minimum} detection range required by any trajectory-planning algorithm to ensure a successful intruder avoidance for all intruder strategies. In general, assumption \ref{as:detection_range} is required to ensure that the intruder gives the STP vehicles ``a chance" to react and avoid it. Hence, for analysis to follow, we assume that assumption \ref{as:detection_range} holds. 

Note that although \eqref{eqn:optAvoidCtrl} gives us a provably successful avoidnace control for avoiding the intruder if $\state_{\intr i}(\tsa) \in \left(\brs^{\text{A}}_{i}(0, \iat)\right)^C$, the vehicle may not be able to apply this control beacuse it may lead to a collision with other STP vehicles. Thus, in general, assumption \ref{as:detection_range} is \textit{only necessary not sufficient} to guarantee intruder avoidance. However, we ensure that the STP vehicles are always separated enough from each other so that any vehicle can apply avoidnace maneuver if need be. Thus, for the proposed algorithm, assumption \ref{as:detection_range} will also be sufficient for a successful intruder avoidance.
%Under normal circumstances when the intruder $\veh_{\intr}$ is far away, we have $\valfunc^{\text{S}}_{i}(0, \state_{\intr i}(t)) > 0$; as $\veh_{\intr}$ gets closer to $\veh_i$, $\valfunc^{\text{S}}_{i}(0, \state_{\intr i}(t))$ decreases. If $\veh_i$ applies the control ${\ctrl^{\text{S}}_{i}}$ when $\valfunc^{\text{S}}_{i}(0, \state_{\intr i}(t)) = 0$, then collision avoidance between $\veh_i$ and $\veh_{\intr}$ is guaranteed for a duration of $\iat$ under the worst-case intruder control strategy $\ctrl_\intr$.