% !TEX root = STP_journal.tex
\section{Conclusions and Future Work}
Guaranteed-safe multi-vehicle trajectory planning is a challenging problem, and previous analyses often either require strong assumptions on the motion of the vehicles or result in a large degree of conservatism. Differential game techniques such as Hamilton-Jacobi (HJ) reachability are ideally suited for guaranteeing goal satisfaction and safety under disturbances, but become intractable for even a small number of vehicles.

Our robust sequential trajectory planning (STP) method assigns a strict priority ordering to vehicles to offer a tractable and practical approach to the multi-vehicle trajectory planning problem. Under the proposed method, a portion of ``space-time'' is reserved for vehicles in the airspace in descending priority order to allow for dense vehicle configurations. Unlike previous priority-based methods, our approach accounts for disturbances and an adversarial intruder. STP reduces the scaling of HJ reachability's computational complexity from exponential to linear with respect to the number of vehicles, while maintaining hard guarantees on goal satisfaction and safety under disturbances. In the presence of a single intruder vehicle, STP still guarantees goal satisfaction and safety with a quadratically scaling computational complexity.

In the future, we plan to investigate ways of guaranteeing a maximum number of vehicles that need to re-plan, combine reachability analysis with other trajectory and path planning methods to improve computation speed, and to better understand the scenarios under which the STP scheme is the most useful by running large-scale simulations.
\vspace{-0.2cm}