% !TEX root = STP_journal.tex
\section{Problem Formulation \label{sec:formulation}}
Consider $\N$ vehicles which participate in the STP process and denote these vehicles as the \textit{STP vehicles} $\veh_i, i = 1, \ldots, \N$. We assume their dynamics are given by

\begin{equation}
\label{eq:dyn}
\begin{aligned}
\dot\state_i &= \fdyn_i(\state_i, \ctrl_i, \dstb_i), t \le \sta_i \\
\ctrl_i &\in \cset_i, \dstb_i \in \dset_i, i = 1 \ldots, \N
\end{aligned}
\end{equation}

\noindent where $\state_i \in \R^{n_i}$ represents the state of vehicle $\veh_i$, $\ctrl_i \in \cset_i$ the control of $\veh_i$, and $\dstb_i \in \dset_i$ the disturbance experienced by $\veh_i$. For convenience, we partition the state $\state_i$ into the position component $\pos_i \in \R^{n_\pos}$ and the non-position component $\npos_i \in \R^{n_i - n_\pos}$: $\state_i = (\pos_i, \npos_i)$.

We assume that the control functions $\ctrl_i(\cdot), \dstb_i(\cdot)$ are drawn from the set of measurable functions. 
For convenience, we will use the sets $\cfset_i, \dfset_i$ to respectively denote the set of functions from which the control and disturbance functions $\ctrl_i(\cdot), \dstb_i(\cdot)$ are drawn. 
We further assume that the flow field $\fdyn_i: \R^{n_i}\times\cset_i\times\dset_i \rightarrow \R^{n_i}$ is uniformly continuous, bounded, and Lipschitz continuous in $\state_i$ for fixed $\ctrl_i$ and $\dstb_i$. With this assumption, given $\ctrl_i(\cdot) \in \cfset_i, \dstb_i(\cdot) \in \dfset_i$, there exists a unique trajectory solving \eqref{eq:dyn} \cite{EarlA.Coddington1955}. 
Finally, we assume that the disturbances $\dstb_i(\cdot)$ are drawn from the set of non-anticipative strategies \cite{Mitchell05} $\Gamma$:
\begin{equation}
\begin{aligned}
& \Gamma := \{\mathcal{N}: \cfset_i \rightarrow \dfset_i:  \ctrl_i(r) = \hat{\ctrl}_i(r) \text{ a. e. } r\in[t,s] \\
& \Rightarrow \mathcal{N}[\ctrl_i](r) = \mathcal{N}[\hat{\ctrl}_i](r) \text{ a. e. } r\in[t,s]\}
\end{aligned}
\end{equation}

Each vehicle $\veh_i$ has initial state $\state^0_i$, and aims to reach its target $\targetset_i$ by some scheduled time of arrival $\sta_i$. The target in general represents some set of desirable states, for example the destination of $\veh_i$. %For most of the paper we will make the assumption that $\edt_i$ is early enough for $\veh_i$ to feasibly get to $\targetset_i$ on time; this can be done by letting $\edt_i \rightarrow -\infty$. The assumption on $\edt_i$ is merely for convenience: in situations where $\edt_i$ is $-\infty$
In some situations, we may find that it is infeasible for $\veh_i$ to get to $\targetset_i$ at or before $\sta_i$. Whenever unsure, we may first determine the earliest feasible $\sta_i$ as described in Section \ref{sec:intruder}. 

On its way to $\targetset_i$, $\veh_i$ must avoid a set of static obstacles $\soset_i \subset \R^{n_i}$. The interpretation of $\soset_i$ could be a tall building, a region around an airport, or any set of states that are forbidden for each STP vehicle. In addition to the static obstacles, each vehicle $\veh_i$ must also avoid the danger zones with respect to every other vehicle $\veh_j, j\neq i$. The danger zones in general can represent any joint configurations between $\veh_i$ and $\veh_j$ that are considered to be unsafe. In this paper, we define the danger zone of $\veh_i$ with respect to $\veh_j$ to be
%
\begin{equation}
\dz_{ij} = \{(\state_i, \state_j): \|\pos_i - \pos_j\|_2 \le \rc\}
\end{equation}
%
\noindent whose interpretation is that $\veh_i$ and $\veh_j$ are considered to be in an unsafe configuration when they are within a distance of $\rc$ of each other. For concreteness, we will call $\dz_{ij}$ the collision set, and if $(\state_i, \state_j) \in \dz_{ij}$, then $\veh_i$ and $\veh_j$ are said to have collided. \SBnote{Note that, for practical system, there might exists an inevitable danger zone given the position-based danger zone $\dz_{ij}$ (for example the states from which wind can push an aerial vehicle in $\dz_{ij}$ irrespective of control applied by the vehicle). However, the reachability analysis presented in this paper can successfully avoid such inevitable danger zones. Finally, if the vehicles are not particles (as often is the case), the danger zone $\dz_{ij}$ can be defined to include the effective sizes of the vehicles.} 

Given the set of STP vehicles, their targets $\targetset_i$, the static obstacles $\soset_i$, and the vehicles' danger zones with respect to each other $\dz_{ij}$, we would like, for each vehicle $\veh_i$, to synthesize a controller which guarantees that $\veh_i$ reaches its target $\targetset_i$ at or before the scheduled time of arrival $\sta_i$, while avoiding the static obstacles $\soset_i$ as well as the danger zones with respect to all other vehicles $\dz_{ij}, j\neq i$. In addition, we would like to obtain the latest departure time $\ldt_i$ such that $\veh_i$ can still arrive at $\targetset_i$ on time. \MCnote{Note that as long as it is feasible a vehicle to reach its target in the \textit{absence} of all other vehicles, producing a safe and timely trajectory is \textit{always} feasible using our proposed algorithms, since the latest departure time $\ldt_i$ is obtained. Indeed, if the environment is expected to be crowded, a vehicle can simply depart early enough (and potentially arrive very early) to ``avoid traffic''. In practice, if departing at or before the latest departure time $\ldt_i$ is not possible, then arriving on time is infeasible.}

In general, the above optimal trajectory planning problem must be solved in the joint space of all $\N$ STP vehicles. However, due to the high joint dimensionality, a direct dynamic programming-based solution is intractable. Therefore, we propose to assign a priority to each vehicle, and perform STP given the assigned priorities. Without loss of generality, let $\veh_j$ have a higher priority than $\veh_i$ if $j<i$. Under the STP scheme, higher-priority vehicles can ignore the presence of lower-priority vehicles, and perform trajectory planning without taking into account the lower-priority vehicles' danger zones. A lower-priority vehicle $\veh_i$, on the other hand, must ensure that it does not enter the danger zones of the higher-priority vehicles $\veh_j, j<i$; each higher-priority vehicle $\veh_j$ induces a set of time-varying obstacles $\ioset_i^j(t)$, which represents the possible states of $\veh_i$ such that a collision between $\veh_i$ and $\veh_j$ could occur.

It is straight-forward to see that if each vehicle $\veh_i$ is able to plan a trajectory that takes it to $\targetset_i$ while avoiding the static obstacles $\soset_i$ and the danger zones of \textit{higher-priority vehicles} $\veh_j, j<i$, then the set of STP vehicles $\veh_i, i=1,\ldots,\N$ would all be able to reach their targets safely. With the STP scheme, the additional structure provided by the vehicle priorities allows us to reduce the complexity of the joint trajectory planning problem. As we will see, under the STP scheme, trajectory planning can be done sequentially in descending order of vehicle priority in the state space of only a single vehicle. Thus, STP provides a solution whose complexity scales linearly with the number of vehicles in the presence of disturbances, as opposed to exponentially with a direct application of dynamic programming approaches. In the presence of a single intruder, the computation complexity scaling becomes quadratic. \MCnote{As mentioned earlier, priorities of vehicles may be assigned in a first-come-first-serve basis through, for example, an air navigation service provider \cite{Kopardekar16} which manages a region of the low altitude airspace.}

In the following sections, we will explore STP under different assumptions. We begin with the basic STP algorithm in which disturbances are ignored and perfect information of vehicles' positions is assumed. This simplification allows us to clearly establish the basic STP algorithm. Next, we show how the basic STP approach can be made robust to disturbances as well as an imperfect knowledge of other vehicles' positions. Finally, we further robustify the STP approach by considering how the set of STP vehicles may respond to the presence of an intruder vehicle which may be adversarial. All of our methods use time-varying reachability analysis to provide goal satisfaction and safety guarantees.